---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vinnova


<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/KTH-Library/vinnova/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KTH-Library/vinnova/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of the R-package `vinnova` is to provide access to open data from [Vinnova - Sweden's Innovation Agency](https://www.vinnova.se/en/about-us). 

The open data APIs from Vinnova covers data about programmes, calls for proposals and application rounds as well as projects that have been funded. The APIs are documented at <https://data.vinnova.se/api/> and this R package uses the open APIs at Vinnova to make data available for use from R, primarily in tabular formats .

## Installation

You can install the development version of vinnova from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("KTH-Library/vinnova")
```

## Example

Basic examples which shows you how to get data.

Fetching "projects" data:

```{r example, message=FALSE}
library(vinnova)
library(dplyr)

# projects from the last three days
three <- vinnova("projects", from_date = Sys.Date() - 3)

# number of rows
nrow(three)

# field names
names(three)

# three items displayed in a table
three %>% slice(1:3) %>% select(1:2) %>% knitr::kable()


```
More context can be retrieved as related tables:

```{r}

vinnova_latest(from_date = Sys.Date())

```



Files can be retrieved:

```{r}

# files from Vinnova
filez <- vinnova_files()

# number of rows
nrow(filez)

# field names
names(filez)

# display result - first few rows... (which could be inserted into a database table)
filez %>% slice(1:5) %>% select("Titel", 1:2, "fileURL") %>% knitr::kable()

```
